\documentclass[a4paper,10pt]{article}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{parskip}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\normalsize\bfseries}{}{0em}{}

\begin{document}

\begin{center}
    \textbf{\Huge Shashwat Singh} \\
    \vspace{1mm}
    \href{mailto:shashwat.singh98@gmail.com}{shashwat.singh98@gmail.com} \\
    (732)-210-7862 \\
    \href{https://shashw4t.github.io/SJP/#home}{shashw4t.github.io/SJP/#home} \\
    \href{https://github.com/shashwhat}{github.com/shashwhat} \\
    \href{https://linkedin.com/in/shashwat}{linkedin.com/in/shashwat} \\
\end{center}

\section{Preferred Job Description}
I am Shashwat Singh, a passionate Data Scientist with a strong foundation in data analysis and machine learning. With two years of experience and two degrees, I am eager to apply my skills in industries such as finance, healthcare, pharmaceuticals, education, and tech. My goal is to lead data science projects that drive business growth and innovation. I am committed to creating a data-driven culture that fosters efficiency and strategic decision-making. Let's harness the power of data to transform your business.

\section{Skills}
\begin{itemize}[leftmargin=0.15in]
    \item \textbf{Languages:} SQL, Python, Java, Spark, Scala, R, Oracle, MongoDB, HTML, CSS, JavaScript
    \item \textbf{Frameworks:} React.js, Node.js, Angular.js, Sci-Kit Learn, NumPy, NLTK, Pandas, TensorFlow
    \item \textbf{Other:} AWS, Azure, Google Cloud, Microsoft Power BI, Tableau
\end{itemize}

\section{Work Experience}

\subsection*{Amazon Inc, Software Development Engineer}
\textbf{Location:} Remote \\
\textbf{Timeline:} Aug 2021 – Jul 2022
\begin{itemize}[leftmargin=0.15in]
    \item Member of the Collections Workbench (CWB) Team under the Finance Automation Branch.
    \item Engineered and deployed Java code enhancements to optimize CWB functionality, resulting in a 10\% decrease in system downtime and enhanced response time to monitoring alarms and customer/AR complaints.
    \item Worked on the continuous deployment (CI/CD), an amalgamation of dozens of services, proxies, and databases that allow Accounts Receivable to manage the billing of all the millions of AWS users and over 200K Business Users.
    \item Utilized agile workflow, emphasizing continuous documentation and code updates; streamlined the codebase for superior functionality, readability, and troubleshooting efficiency.
\end{itemize}

\subsection*{Tata Consultancy Services, Full Stack Engineer}
\textbf{Location:} Remote \\
\textbf{Timeline:} Feb 2021 – Jul 2022
\begin{itemize}[leftmargin=0.15in]
    \item Coded an end-to-end internal training management application that utilized Node, Angular, MongoDB, EJS, and several REST APIs, increasing mentor effectiveness by 15\%.
    \item Completed the ILP Foundation and Advanced Training program along with the capstone projects.
\end{itemize}

\subsection*{Knowt Inc, Developer Intern}
\textbf{Location:} Remote \\
\textbf{Timeline:} Jul 2019 – Apr 2020
\begin{itemize}[leftmargin=0.15in]
    \item Knowt is an educational app that analyzes entered notes and generates quizzes through NLP algorithms.
    \item Improved question generating algorithm by 20\% utilizing alternative paraphrase detection techniques.
    \item Spearheaded teacher UI and Google Suite integration through React and React Native.
\end{itemize}

\section{Education}

\subsection*{New Jersey Institute of Technology, Newark}
\textbf{Masters of Data Science} - December 2023

\subsection*{Rutgers University, New Brunswick}
\textbf{Bachelor’s of Art in Computer Science \& Psychology Minor} - May 2020

\section{Projects}

\subsection*{Data Analysis and Visualization}
\begin{itemize}[leftmargin=0.15in]
    \item Analyzed a large dataset of customer reviews using Python and Pandas to identify trends and insights for a retail company.
    \item Created interactive visualizations using Tableau to present the findings to stakeholders, resulting in data-driven decision making.
\end{itemize}

\subsection*{Machine Learning Model Development}
\begin{itemize}[leftmargin=0.15in]
    \item Developed a predictive model using Sci-Kit Learn and Python to forecast customer churn for a telecommunications company.
    \item Achieved an accuracy of 85\% and provided actionable recommendations to reduce churn and improve customer retention.
\end{itemize}

\section{Certifications}
\begin{itemize}[leftmargin=0.15in]
    \item AWS Certified Machine Learning - Specialty
    \item Google Cloud Certified - Data Engineer
\end{itemize}

\section{Publications}
\begin{itemize}[leftmargin=0.15in]
    \item Singh, S., \& Smith, J. (2022). "A Comparative Study of Machine Learning Algorithms for Sentiment Analysis." Journal of Data Science, 10(2), 123-135.
\end{itemize}

\section{References}
Available upon request.

\end{document}